Enhancement of SDR in Thessaloniki

### 2024-07-05 GHI_enh_04_investigate.tex
Commit 2024-07-05 11:10

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-06-27}

@@

\caption{ - empty caption - }\label{fig:groups-1}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-2}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-4}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-7}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-8}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-11}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-12}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-14}

\caption{ - empty caption - }\label{fig:groups-14}
\end{figure}

@@

\begin{verbatim}
2024-06-27 02:44:09.1 athan@tyler GHI_enh_04_investigate.R 2.523809 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-07-05}

@@

\caption{ - empty caption - }\label{fig:groups-1}
\end{figure}

\begin{verbatim}
Warning in annotate("segment", x = 25, xend = 50, y = 3, yend = 15, colour =
"pink", : Ignoring unknown parameters: `line`
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-2}
\end{figure}
\begin{figure}[H]

@@

@@

\caption{ - empty caption - }\label{fig:groups-5}
\end{figure}

\begin{verbatim}
Warning: Removed 229 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 28216 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-6}
\end{figure}

\begin{verbatim}
Warning: Removed 229 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 28216 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\caption{ - empty caption - }\label{fig:groups-7}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-8}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-11}
\end{figure}

@@

\caption{ - empty caption - }\label{fig:groups-12}
\end{figure}
\begin{figure}[H]

@@

\caption{ - empty caption - }\label{fig:groups-13}
\end{figure}

@@

\begin{verbatim}
2024-07-05 07:51:29.9 athan@tyler GHI_enh_04_investigate.R 2.549931 mins
\end{verbatim}
